Pilot data analysis

### 2021-04-02 Manuscript_intro_method_results.Rmd
Add method and results

---
title             : |
    | Can we use masked priming in an online setting?
    | The effect of prime exposure duration in online masked priming lexical decision
shorttitle        : "Online masked priming"

author: 
  - name          : "Bernhard Angele"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Psychology, Faculty of Science and Technology, Talbot Campus, Fern Barrow, Poole BH12 5BB, UK"
    email         : "bangele@bournemouth.ac.uk"
  - name          : "Ana Baciero"
    affiliation   : "2,3"
  - name          : "Pablo Gomez"
    affiliation   : "4"
  - name          : "Manuel Perea Lara"
    affiliation   : "2,5"

affiliation:
  - id            : "1"
    institution   : "Bournemouth University, Bournemouth, UK"
  - id            : "2"
    institution   : "Universidad Antonio de Nebrija, Madrid, Spain"
  - id            : "3"
    institution   : "DePaul University, Chicago, USA"
  - id            : "4"
    institution   : "California State University San Bernardino, Palm Desert Campus, USA"
  - id            : "5"
    institution   : "Universitat de Valencia, Valencia, Spain"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

@@

keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
wordcount         : "XXX"

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
bibliography: ["references.bib", "r-references.bib"]
---

```{r setup, include = FALSE}
library("papaja")
library("tidyverse")
library("brms")
r_refs("r-references.bib")

@@

The masked priming paradigm has been used in a large number of studies over the last decades. For instance, a search of the expression "masked priming" in Google Scholar in March 2021 produced nearly 10,000 hits. Virtually all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003). The issue we examine in the present paper is whether masked priming experiments can safely be conducted in an online setting. Even before the current exceptional situation due to the COVID pandemic, in which many labs around the world have been closed (or with minimal activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc. Indeed, researchers in decision making and economics have been using online paradigms for several decades now [e.g., @birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010].

@@

To further constraint the research questions, Experiment 2 was parallel to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.6ms). Similar prime exposure durations have shown rather weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for a prime durations of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen. Thus, if prime exposure durations in online masked priming correspond to the nominal ones, we would expect a sizeable priming effect at the 33.3 but only a residual priming effect at the 16.6 ms prime exposure duration. Alternatively, if we obtain a sizeable effect at the 16.6 ms prime exposure duration (e.g., above 20-25 ms), this would indicate, again, that we should be wary of using the masked priming technique in online experiments. Keep in mind that we are using a software that has good control over the exposure duration (\color{red} CITE).

@@

We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

@@

```{r load_exp1_data, message=FALSE, echo=FALSE}
library(xfun)
library(tidyverse)
library(sp)
library(rworldmap)

e1_all_participants <- read_csv("participant_data_exp1.csv")

e1 <- read_csv(file = "Exp 1 data.csv")

@@

e1_actual_participants <- filter(e1_all_participants, PROLIFIC_PID %in% e1$participant & `What is your age?` != 99 & `Response ID` != "R_sU4qJ6UCe9jRKs9")

participant_ages <- e1_actual_participants$`What is your age?`

male_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow

female_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow

# there aren't actually any of these, but will leave the code in just in calse
other_participants_nr <- filter(e1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow

NA_participants_nr <- filter(e1_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow

#coordinates(e1_actual_participants) <- c("Location Longitude","Location Latitude")

@@

participant_coords <- e1_actual_participants %>% select("Location Longitude", "Location Latitude")

e1_actual_participants$country <- coords2country(participant_coords)

e1_participant_countries <- table(e1_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
```

@@

We collected data from `r e1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants aged from `r participant_ages %>% min` to `r participant_ages %>% max` (mean age: `r participant_ages %>% mean %>% round(2)`) recruited through Prolific [www.prolific.co, -@prolific2021]. Of the participants, `r male_participants_nr` identified as male and `r female_participants_nr` identified as female. The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions. Based on their IP addresses, `r e1_participant_countries["United Kingdom"] %>% ifelse(. < 11, numbers_to_words(.), .)` participants were based in the UK, `r e1_participant_countries["United States of America"] %>% ifelse(. < 11, numbers_to_words(.), .)` were based in the US, `r e1_participant_countries["Canada"] %>% ifelse(. < 11, numbers_to_words(.), .)` participants were based in Canada, and `r e1_participant_countries["Ireland"] %>% ifelse(. < 11, numbers_to_words(.), .)` participants were based in Ireland. Two participants could not be localized in this way. Participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour). All participants were naïve to the purpose of the experiment. Participants could use a desktop or laptop computer or a mobile device. Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.

@@

We selected 240 six-letter English words from the English Lexicon Project [@balota2007]. The mean Zipf frequency based on the HAL corpus [@lund1996] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(Freq_HAL %>% log10)) %>% signif(2)` (range: `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(Freq_HAL %>% log10)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(Freq_HAL %>% log10)) %>% signif(2)`). The mean OLD20 [@yarkoni2008] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(OLD)) %>% signif(2)`(range:`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(OLD)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(OLD)) %>% signif(2)`). We also selected 240 matched, orthographically legal six-letter nonwords. For each target, we created an identical prime (e.g.`region`--`REGION`and`fainch`--`FAINCH`) and an unrelated prime consisting of another word from the list (e.g.`launch`--`REGION`and`miluer`--`FAINCH`). Appendix A contains a list of the items.

@@

Participants were able to sign up for the experiment on the Prolific website. On signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment [@qualtrics2020]. After indicating their agreement to participate, participants were forwarded to Pavlovia [@pavlovia2020], where the actual PsychoJS experiment was hosted. In the experiment, all stimuli were presented in the center of the screen in black Courier New font on a white background. As we do not know the exact dimensions of each participant's screen, all stimulus sizes and positions were defined in Psychopy's "height" units, with the bottom left of a 16:10 aspect ratio screen being represented as (-.8, -.5) and the top right being (.8, .5). The height for all text stimuli was 0.1 units. Each trial began with a six-character pattern mask (`######`) set to be presented for 500 ms, followed first by the lowercase prime (e.g. `region`) set to be presented for either 33 or 50 ms, and then by the uppercase target (e.g. `REGION`). Participants were instructed to respond to the target stimulus as quickly as possible either by using the keyboard, if their device had one, and pressing the "Z" key if the target was not a valid English word or the "M" key if the target was a valid English word. Participants on a device without a keyboard were instructed to respond by touching one of two rectangular touch areas labeled "Z = Non-word" (presented at -0.4, -0.3) and "M = Word" (presented at 0.4, -0.3). The touch areas each had a width of 0.4 and a height of 0.2 and were presented in white with a black outline. If participants did not respond within two seconds of the target onset, a "Too slow!" feedback message was shown for 500 ms and the trial ended. The experimental trials were preceded by 16 practice trials during which participants also received feedback on the accuracy of their responses. No feedback apart from the trial timeout feedback was given during the experimental trials. Every 120 trials, participants were asked to take a short break before continuing the experiment. After completing the experiment, participants were redirected to a debriefing form on Qualtrics and from there back to Prolific in order to receive their participation payment.

@@

We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the *brms* package [@R-brms_a; @R-brms_b] in R [@R-base][^1].

@@

We

@@

```{r exp1_descriptive_rt_table, as.is = TRUE,echo=FALSE}
#load raw Exp1 data
exp1 <- read_csv("Exp 1 data.csv")
exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")

exp1$StimulusType <- factor(exp1$StimulusType, levels = c("NW", "WORD"), labels = c("Nonword", "Word"))
exp1$Condition <- factor(exp1$Condition, levels = c("ID", "UN"), labels = c("Identical", "Unrelated"))
exp1$PrimeDuration <- factor(exp1$PrimeDuration, levels = c(33, 50), labels = c("33 ms", "50 ms"))

exp1_descriptives_rt <- exp1 %>%
  filter(rt > 250 & rt < 2000 & corr == 1) %>%
  group_by(StimulusType, PrimeDuration, Condition) %>%
  summarize(
    Mean = mean(rt)
    , Median = median(rt)
    , SD = sd(rt)
    , Min = min(rt)
    , Max = max(rt)
  )

exp1_descriptives_corr <- exp1 %>%
  filter(rt > 250 & rt < 2000) %>%
  group_by(StimulusType, PrimeDuration, Condition) %>%
  summarize(
    Accuracy = mean(corr)
  )

@@

apa_table(
  exp1_descriptives_rt
  , caption = "(ref:exp1-descriptives-rt-table-caption)"
  , note = "Trials with reaction times below 250 ms were excluded from the analysis. For the calculation of response times, incorrect responses were also removed."
  , escape = TRUE
)  
```
We

(ref:exp1-blmm-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 1.

```{r load_exp1_brms_data, echo=FALSE, as.is = TRUE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
load("blmm_exp1_rt_new.RData")
# model name is blmm_exp1_rt

@@

blmm_exp1_summary <- summary(blmm_exp1_rt)

blmm_exp1_fixed_for_print <- blmm_exp1_summary$fixed

@@

blmm_exp1_fixed_for_print <- blmm_exp1_fixed_for_print %>% tibble(Parameter = parameter_names, .)

colnames(blmm_exp1_fixed_for_print) <- c("mean","SE","lower bound","upper bound","Rhat", "Bulk ESS","Tail ESS")

blmm_exp1_fixed_for_print <- blmm_exp1_fixed_for_print  %>%
  dplyr::select(-ends_with("ESS"))

write.csv(blmm_exp1_fixed_for_print, file = "Table_1.csv", row.names = FALSE)

apa_table(
    blmm_exp1_fixed_for_print,
    placement = "H",
    align = c("c", "c", "c", "c", "c"),
    caption = "(ref:exp1-blmm-table-caption)",
    note = NULL,
    small = TRUE,
    digits = 3,
    escape = FALSE
    )

@@

@@

>>>>

---
title             : |
    | Can we use masked priming in an online setting?
    | The effect of prime exposure duration in online masked priming lexical decision
shorttitle        : "Online masked priming"
author: 
  - name          : "Bernhard Angele"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Department of Psychology, Faculty of Science and Technology, Talbot Campus, Fern Barrow, Poole BH12 5BB, UK"
    email         : "bangele@bournemouth.ac.uk"
  - name          : "Ana Baciero"
    affiliation   : "2,3"
  - name          : "Pablo Gomez"
    affiliation   : "4"
  - name          : "Manuel Perea Lara"
    affiliation   : "2,5"
affiliation:

  - id            : "1"
    institution   : "Bournemouth University, Bournemouth, UK"
  - id            : "2"
    institution   : "Universidad Antonio de Nebrija, Madrid, Spain"
  - id            : "3"
    institution   : "DePaul University, Chicago, USA"
  - id            : "4"
    institution   : "California State University San Bernardino, Palm Desert Campus, USA"
  - id            : "5"
    institution   : "Universitat de Valencia, Valencia, Spain"
authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.
  Enter author note here.

@@

keywords          : "Masked priming, Lexical decision task, Online experiments, PsychoPy, Prime duration"
wordcount         : "XXX"
floatsintext      : yes
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no
documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
bibliography: ["references.bib", "r-references.bib"]
editor_options: 
  chunk_output_type: console
---

```{r setup, include = FALSE}
library("tidyverse")
library("brms")
library("bayestestR")
library("see")
library("papaja")

r_refs("r-references.bib")

@@

The masked priming paradigm has been used in a large number of studies over the last decades. For instance, a search of the expression "masked priming" in Google Scholar in March 2021 produced nearly 10,000 hits. Virtually all masked priming experiments have been run in a laboratory setting, often using the DMDX software developed by @forsterDMDXWindowsDisplay2003. The issue we examine in the present paper is whether masked priming experiments can safely be conducted in an online setting. Even before the current exceptional situation due to the COVID pandemic, in which many labs around the world have been closed (or with minimal activity) for many months, online data collection has shown its many advantages: 1) easy access to a much more diverse population than that accessible at the typical university research laboratory; 2) independence from laboratory space constraints, and, often, lower costs as participants only need to be compensated for their time on the experiment; 3) no time spent commuting, waiting for the experiment to start, etc. Indeed, researchers in decision making and economics have been using online paradigms for several decades now [e.g., @birnbaumPsychologicalExperimentsInternet2000a; @paolacciRunningExperimentsAmazon2010].

@@

To further constraint the research questions, Experiment 2 was parallel to Experiment 1, except for the use of a very short prime exposure duration (i.e., 16.6ms). Similar prime exposure durations have shown rather weak masked priming lexical decision experiments in a laboratory setting: smaller than 5 ms for prime durations of 14 ms [@ziegler2000] and smaller than 9 ms for a prime duration of 20 ms [@Tzur_2007]---in the @Tzur_2007 experiment, this difference increased to 16 ms when using a very high level of contrast in the computer screen. Thus, if prime exposure durations in online masked priming correspond to the nominal ones, we would expect a sizeable priming effect at the 33.3 but only a residual priming effect at the 16.6 ms prime exposure duration. Alternatively, if we obtain a sizeable effect at the 16.6 ms prime exposure duration (e.g., above 20-25 ms), this would indicate, again, that we should be wary of using the masked priming technique in online experiments. Keep in mind that we are using a software that has good control over the exposure duration (\color{red} CITE).

@@

We report here how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the two experiments. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

@@

```{r load_exp1_data, message=FALSE, echo=FALSE, warning=FALSE}
library(xfun)
library(tidyverse)
library(sp)
library(rworldmap)

# Qualtrics survey data
exp1_all_participants <- read_csv("participant_data_exp1.csv")

# PsychoJS trial data
exp1 <- fs::dir_ls(path = "./data_exp1", glob = "*.csv") %>%
  map_dfr(read_csv, .id = "source", col_type = cols(
  .default = col_character(), rt = col_double(), corr = col_integer(), TrialID = col_integer())) %>% 
  filter(!is.na(TrialID) & TrialID < 1000) %>%
  select(source, participant, date, OS, frameRate, rt, corr, TrialID, StimulusType, Condition, PrimeDuration, Prime, Target)

exp1$device <- ifelse(exp1$OS %in% c("Linux armv7l", "Linux armv8l"), "android", "computer")

@@

exp1_actual_participants <- filter(exp1_all_participants, (PROLIFIC_PID %in% exp1$participant) & (nchar(PROLIFIC_PID) == 24) & !(PROLIFIC_PID %in% c("5fa3b4abbcfd0b6c243758bc")) & (`What is your age?` != 99) & (`Response ID` != "R_sU4qJ6UCe9jRKs9"))

# get participants with more than 80% correct responses

exp1_accuracy_by_participant <- exp1 %>% filter(participant %in% exp1_actual_participants$PROLIFIC_PID) %>% group_by(source) %>% summarise(acc = mean(corr == 1), N = n())

exp1_participants_to_include <- exp1_accuracy_by_participant %>% filter(N == 480 & acc >= .8)

exp1_participants_to_exclude <- exp1_accuracy_by_participant %>% filter(N != 480 | acc < .8)

#participant_list_for_prolific <- str_extract(string = participants_to_include$source, pattern = "[a-z0-9]{24}")

exp1_data_to_include <- exp1 %>% filter(source %in% exp1_participants_to_include$source & participant %in% exp1_actual_participants$PROLIFIC_PID) %>% mutate(StimulusType = StimulusType %>% factor(levels = c("NW", "WORD"), labels = c("Nonword", "Word")), Condition = Condition %>% factor(levels = c("ID", "UN"), labels = c("Identical", "Unrelated")), PrimeDuration = PrimeDuration %>% factor(levels = c(33, 50), labels = c("33 ms", "50 ms")), rt = rt * 1000)

# filter out any of the participants we eliminated from the Qualtrics file as well

exp1_actual_participants <- filter(exp1_actual_participants, (PROLIFIC_PID %in% exp1_data_to_include$participant))

exp1_participant_ages <- exp1_actual_participants$`What is your age?`

exp1_male_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Male") %>% nrow

exp1_female_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Female") %>% nrow

# there aren't actually any of these, but will leave the code in just in case
exp1_other_participants_nr <- filter(exp1_actual_participants, `What is your gender (optional)?` == "Other") %>% nrow

exp1_NA_participants_nr <- filter(exp1_actual_participants, is.na(`What is your gender (optional)?`)) %>% nrow

exp1_participant_coords <- exp1_actual_participants %>% select("Location Longitude", "Location Latitude")

#coordinates(exp1_actual_participants) <- c("Location Longitude","Location Latitude")

@@

participant_coords <- exp1_actual_participants %>% select("Location Longitude", "Location Latitude")

exp1_actual_participants$country <- coords2country(participant_coords)

exp1_participant_countries <- table(exp1_actual_participants$country %>% as.character) #make into a character vector since the original output is a factor with as many levels as there are countries
```

@@

Participants were recruited through Prolific [www.prolific.co, -@prolific2021]. The experiment was accessed by `r exp1_all_participants$PROLIFIC_PID %>% unique %>% length` participants. Out of these, `r exp1_accuracy_by_participant %>% nrow` provided experimental data. `r exp1_participants_to_exclude %>% filter(N != 480) %>% nrow %>% numbers_to_words() %>% str_to_sentence()` of these participants did not complete the experiment. A further `r exp1_participants_to_exclude %>% filter(N == 480 & acc < .8) %>% nrow %>% ifelse(. < 11, numbers_to_words(.), .)` were excluded because of low accuracy (less than .8). The remaining `r exp1_actual_participants$PROLIFIC_PID %>% unique %>% length` participants were aged from `r exp1_participant_ages %>% min` to `r exp1_participant_ages %>% max` (mean age: `r exp1_participant_ages %>% mean %>% round(2)`). Of the participants, `r exp1_male_participants_nr` identified as male and `r exp1_female_participants_nr` identified as female. The experiment was only shown to participants who indicated that English was their first language in the Prolific screening questions. Based on their IP addresses, `r exp1_participant_countries["United Kingdom"] %>% ifelse(. < 11, numbers_to_words(.), .)` participants were based in the UK, `r exp1_participant_countries["United States of America"] %>% ifelse(. < 11, numbers_to_words(.), .)` were based in the US, `r exp1_participant_countries["Canada"] %>% ifelse(. < 11, numbers_to_words(.), .)` participants were based in Canada, and `r exp1_participant_countries["Ireland"] %>% ifelse(. < 11, numbers_to_words(.), .)` participants were based in Ireland. Two participants could not be localized in this way. Participants who completed the experiment were paid £1.25 for their participation (corresponding to £5/hour). All participants were naïve to the purpose of the experiment. Participants could use a desktop or laptop computer or a mobile device. Because of a technical display issue with PsychoJS and the Safari browser, participants who tried to access the experiment using that browser, including all participants on iOS devices, were advised to change browser or device and restart the experiment.

#### Rationale for sample size and stopping rule

@brysbaert2018 recommended that masked priming experiments should have at least 1,600 observations per condition. In order to account for potentially smaller effect sizes in an online experiment, we set a target of 3,000 observations per condition (12,000 observations total), which corresponds to a minimum of 50 participants given that there were 240 word stimuli in the experiment (see below). Our stopping rule was to keep collecting data until 3,000 valid observations were found. This goal was met and exceeded in our initial data collection with a budget of £200.

@@

We selected 240 six-letter English words from the English Lexicon Project [@balota2007]. The mean Zipf frequency based on the HAL corpus [@lund1996] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(Freq_HAL %>% log10)) %>% signif(2)` (range: `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(Freq_HAL %>% log10)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(Freq_HAL %>% log10)) %>% signif(2)`). The mean OLD20 [@yarkoni2008] was `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(mean = mean(OLD)) %>% signif(2)` (range: `r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(min = min(OLD)) %>% signif(2)`--`r trials_word_stats %>% filter(StimulusType == "WORD") %>% summarise(max = max(OLD)) %>% signif(2)`). We also selected 240 matched, orthographically legal six-letter nonwords. For each target, we created an identical prime (e.g. `region` --- `REGION` and `fainch` --- `FAINCH`) and an unrelated prime consisting of another word from the list (e.g. `launch` --- `REGION` and `miluer` --- `FAINCH`). Appendix A contains a list of the items.

@@

Participants were able to sign up for the experiment on the Prolific website. On signing up, they were redirected to the participant agreement form on the Qualtrics online survey development environment [@qualtrics2020]. After indicating their agreement to participate, participants were forwarded to Pavlovia [@pavlovia2020], where the actual lexical decision task was implemented in PsychoJS. In the experiment, all stimuli were presented in the center of the screen in black Courier New font on a white background. As we do not know the exact dimensions of each participant's screen, all stimulus sizes and positions were defined in Psychopy's "height" units, with the bottom left of a 16:10 aspect ratio screen being represented as (-.8, -.5) and the top right being (.8, .5). The height for all text stimuli was 0.1 units. Each trial began with a six-character pattern mask (`######`) set to be presented for 500 ms, followed first by the lowercase prime (e.g. `region`) set to be presented for either 33 or 50 ms, and then by the uppercase target (e.g. `REGION`). Participants were instructed to respond to the target stimulus as quickly as possible either by using the keyboard, if their device had one, and pressing the "Z" key if the target was not a valid English word or the "M" key if the target was a valid English word. Participants on a device without a keyboard were instructed to respond by touching one of two rectangular touch areas labeled "Z = Non-word" (presented at -0.4, -0.3) and "M = Word" (presented at 0.4, -0.3). The touch areas each had a width of 0.4 and a height of 0.2 and were presented in white with a black outline. If participants did not respond within two seconds of the target onset, a "Too slow!" feedback message was shown for 500 ms and the trial ended. The experimental trials were preceded by 16 practice trials during which participants also received feedback on the accuracy of their responses. No feedback apart from the trial timeout feedback was given during the experimental trials. Every 120 trials, participants were asked to take a short break before continuing the experiment. After completing the experiment, participants were redirected to a debriefing form on Qualtrics and from there back to Prolific in order to receive their participation payment.

@@

We analyzed the data by fitting Bayesian linear and generalized linear mixed models, using the *brms* package [@R-brms_a; @R-brms_b] in R [@R-base][^1]. We only analyzed trials where the target stimulus was a word. For the response time (RT) analysis, we excluded trials with RTs lower than 250 ms and incorrect responses (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000 | corr == 0))/nrow(.)}*100` % of trials). For the accuracy analysis, we only excluded trials with RTs lower than 250 ms (`r exp1_data_to_include %>% filter(StimulusType == "Word") %>% {nrow(filter(., rt < 250 | rt > 2000))/nrow(.)}*100` % of trials). As the trials automatically ended after 2000 ms, there were no RTs longer than this. For both RTs and accuracy, we fitted a model with priming condition (unrelated vs. identical) and prime duration (33 ms vs. 50 ms) as well as their interaction as the fixed effects. For the discrete predictors, we used contrasts as follows: For priming condition, identical was coded as -1 and unrelated was coded as 1. For priming duration, 33 ms was coded as -1 and 50 ms was coded as 1. We used the maximal random effects structure possible, with random intercepts and slopes for condition, prime duration, and the interaction for participants and items. We used the ex-Gaussian distribution to model response times and the Bernoulli distribution (with a logit link) to model response accuracy. We used the default priors suggested by *brms* except for the coefficients for the fixed effects, for which we applied weakly informative priors of $\beta \sim N(0,100)$ in order to rule out improbably large effect sizes. Each model was fitted using four chains with 5000 iterations each (1000 warmup iterations). We consider an effect as credible if the 95% credible interval (CrI) estimated from the posterior distribution does not contain zero.

@@

Descriptive statistics for response times and accuracy for both words and nonwords in the experimental conditions are reported in Table \@ref(tab:exp1-descriptive-rt-table) (although note that we only analyzed the word trials).

@@

```{r exp1-descriptive-rt-table, as.is = TRUE,echo=FALSE}
#load raw Exp1 data

#exp1 <- read_csv("Exp 1 data.csv")

exp1_descriptives_rt <- exp1_data_to_include %>%
  filter(rt > 250 & rt < 2000 & corr == 1) %>%
  group_by(StimulusType, PrimeDuration, Condition) %>%
  summarize(
    Mean = mean(rt)
    , Median = median(rt)
    , SD = sd(rt)
    , Min = min(rt)
    , Max = max(rt)
  )

exp1_descriptives_corr <- exp1_data_to_include %>%
  filter(rt > 250 & rt < 2000) %>%
  group_by(StimulusType, PrimeDuration, Condition) %>%
  summarize(
    Accuracy = mean(corr)
  )

@@

apa_table(
  exp1_descriptives_rt
  , caption = "(ref:exp1-descriptives-rt-table-caption)"
  , note = "Trials with reaction times below 250 ms were excluded from the analysis. For the calculation of response times, incorrect responses were also removed."
  , escape = TRUE
)  
```

### Response times

Table \@ref(tab:exp1-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% credible interval (CrI) of the estimate of each fixed effect in the RT model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.

(ref:exp1-blmm-table-caption) Posterior mean, standard error (SE), 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for correct word response times in Experiment 1.

```{r exp1-blmm-table, echo=FALSE, as.is = TRUE}
# We fit the models in a separate file to make sure that knitting the manuscript doesn't take too long
load("blmm_exp1_rt_new.RData")
# model name is blmm_exp1_rt

@@

blmm_exp1_summary_rt <- summary(blmm_exp1_rt)

blmm_exp1_rt_fixed_for_print <- blmm_exp1_summary_rt$fixed

@@

blmm_exp1_rt_fixed_for_print <- blmm_exp1_rt_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
  dplyr::select(-ends_with("ESS"))

write.csv(blmm_exp1_rt_fixed_for_print, file = "Table_1.csv", row.names = FALSE)

apa_table(
    blmm_exp1_rt_fixed_for_print,
    placement = "H",
    align = c("c", "c", "c", "c", "c"),
    caption = "(ref:exp1-blmm-table-caption)",
    note = NULL,
    small = TRUE,
    digits = 3,
    escape = FALSE
    )

@@

The RT model indicates that response times were higher in the unrelated condition than the identical (*b* = `r blmm_exp1_summary_rt$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1","u-95% CI"]`]) and higher in the 33 ms prime duration condition than in the 50 ms prime duration condition (*b* = `r blmm_exp1_summary_rt$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["PrimeDuration1","u-95% CI"]`]). The interaction term indicates that the priming effect was stronger in the 50 ms condition than the 33 ms condition (*b* = `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_rt$fixed["Condition1:PrimeDuration1","u-95% CI"]`]). Figure \@ref(fig:exp1-brms-rt-plot) shows the posterior distributions of the fixed effects parameters, with various highest density intervals highlighted.

(ref:exp1-brms-rt-plot-caption) 50%, 75%, 89%, 95%, and 100% highest density intervals (HDIs) of the posterior distributions for each of the parameters of the response time model in Experiment 1.

```{r exp1-brms-rt-plot, echo=FALSE, cache=TRUE, fig.cap = "(ref:exp1-brms-rt-plot-caption)"}

del_hdi_exp1_rt = hdi(blmm_exp1_rt, ci = c(0.5, 0.75, 0.89, 0.95))

plot(del_hdi_exp1_rt) + scale_fill_flat() + theme_apa()
```

### Accuracy

Table \@ref(tab:exp1-acc-blmm-table) shows the mean, standard error, lower and upper bounds of the 95% credible interval (CrI) of the estimate of each fixed effect in the accuracy model, as well as the $\hat{R}$ for each estimate, which indicate that the model was fitted successfully as they are all close to 1.

(ref:exp1-blmm-accuracy-table-caption) Posterior mean, standard error, 95% credible interval and $\hat{R}$ statistic for the fixed effects of the model fitted for response accuracy on word trials in Experiment 1.

```{r exp1-acc-blmm-table, echo=FALSE, as.is = TRUE}

load("blmm_exp1_acc_new.RData")

blmm_exp1_summary_acc <- summary(blmm_exp1_acc)

blmm_exp1_acc_fixed_for_print <- blmm_exp1_summary_acc$fixed

blmm_exp1_acc_fixed_for_print <- blmm_exp1_acc_fixed_for_print %>% as_tibble %>% cbind(Parameter = parameter_names, .) %>% 
  `colnames<-`(c("Parameter","mean","SE","lower bound","upper bound","$\\hat{R}$", "Bulk ESS","Tail ESS")) %>%
  dplyr::select(-ends_with("ESS"))

write.csv(blmm_exp1_acc_fixed_for_print, file = "Table_3.csv", row.names = FALSE)

apa_table(
    blmm_exp1_acc_fixed_for_print,
    placement = "H",
    align = c("c", "c", "c", "c", "c"),
    caption = "(ref:exp1-blmm-accuracy-table-caption)",
    note = NULL,
    small = TRUE,
    digits = 3,
    escape = FALSE
    )

The accuracy model indicates that participants were less likely to produce a correct response in the unrelated condition than the identical condition (*b* = `r blmm_exp1_summary_acc$fixed["Condition1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["Condition1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["Condition1","u-95% CI"]`]). The mean of the posterior distribution for prime duration suggests that accuracy was was slightly lower in the 33 ms prime duration condition than in the 50 ms prime duration condition, but as the CrI included 0, this is not credible (*b* = `r blmm_exp1_summary_acc$fixed["PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["PrimeDuration1","u-95% CI"]`]). The interaction term indicates that the effect of priming condition on response accuracy (with the identical condition leading to higher accuracy) was stronger in the 50 ms condition than the 33 ms condition (*b* = `r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","Estimate"]`, 95% CrI [`r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","l-95% CI"]`, `r blmm_exp1_summary_acc$fixed["Condition1:PrimeDuration1","u-95% CI"]`]).

## Discussion

The results from Experiment 1 show that we were able to replicate masked priming effects using an online experiment. The size of the effect is similar to that observed in previous studies. We also saw a clear difference between the 33 ms prime duration and the 50 ms prime duration, indicating that the experiment can reliably implement timing differences of up to one frame across a variety of participant devices. Of course, just because there was a difference between the conditions, this does not necessarily mean that the timings in the two prime duration conditions actually corresponded to the display durations set in the experiment script, just that they were different. In order to further explore this, we perfomed a second experiment in which we set the prime to be displayed for an even shorter duration. As described above, a 16 ms prime duration should yield qualitatively different effects from the 33 and 50 ms durations used in Experiment 1. If it does not, this casts doubt on the timing accuracy in online experiments.

@@

```{r load-exp2-data, as.is = TRUE,echo=FALSE, warning=FALSE}
#load raw Exp2 data

exp2_all_participants <- read_csv("participant_data_exp2.csv")
